---
title: "ICU Status Report"
author: "Yixun Chen"
format: html
editor: visual
excute:
echo: false
message: false
warning: false
---

#### Time and Date of Report

```{r}
time <- Sys.time()
```

```{r}
library(tidyverse)
library(googledrive)
library(kableExtra)
library(plotly)
library(lubridate)
library(knitr)
library(ggplot2)
source("sepsis_monitor_functions.R")
```

```{r}
id <- "1sa9YFpnX9P6p9Io1kzmJ9x6My66qtPMw"
## All data up until now
new_data <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", id))
## Include only most recent data
most_recent_data <- new_data %>%
  group_by(PatientID) %>%
  filter(obsTime == max(obsTime))
```

#### A table listing the patients who currently have sepsis (if any), along with their most recent heart rate, temperature, and respiratory rate

```{r}
sepsis <- most_recent_data %>% 
  subset(most_recent_data$SepsisLabel == 1) 

table1 <- sepsis %>%
  select("Patient ID" = PatientID, "Heart Rate" = HR, "Temperature" = Temp, "Respiratory Rate" = Resp) %>% 
  kable() 
table1

```

#### Plots for all patients who have sepsis (if any) that show the complete history of their heart rate, temperature, and respiratory rate during their time in the ICU. 

```{r}
sepsis_all <- new_data %>% 
  group_by(new_data$PatientID) %>%
  subset(new_data$SepsisLabel == 1) 
sepsis_all %>%
  ggplot() +
  geom_line(aes(x = ICULOS, y = HR, group = PatientID,
                color = "red"), alpha = 1.0) +
  labs(x = "Time ",
       y = "Heart Rate",
       color = "PatientID",
       title = "Heart Rate for Septic Patients")
sepsis_all %>%
  ggplot() +
  geom_line(aes(x = ICULOS, y = Resp, group = PatientID,
                color = "green"), alpha = 1.0) +
  labs(x = "Time in ICU",
       y = "Respiratory Rate",
       color = "PatientID",
       title = "Respiratory Rate for Septic Patients")
sepsis_all %>%
  ggplot() +
  geom_line(aes(x = ICULOS, y = Temp, group = PatientID,
                color = PatientID), alpha = 1.0) +
  labs(x = "Time (Hours) in ICU",
       y = "Temperature",
       title = "Temperature for Septic Patients") 
 
```

#### A table showing the *change* in heart rate, temperature, and respiratory rate between the last two measurements for all patients

```{r}
sepsis_change <- sepsis_all %>% 
  slice_tail(n = 2) %>% 
  summarise( HR_change = last(HR) - first(HR), Temp_change = last(Temp) - first(Temp), Resp_change = last(Resp) - first(Resp) ) 

sepsis_change %>% kable()
```
